Einstein's gravity from a polynomial affine model

### 2015-10-20 AffGR-PRD.tex
Cleaning up

The Eq.~\eqref{SimpleEOM} is related through the second Bianchi identity to the harmonic curvature condition~\cite{bourguignon1981varietes},
\begin{equation}
  \label{harm-curv}
  \nabla_\lambda R_{\mu\nu}{}^\lambda{}_\rho = 0,
\end{equation}
and it can be shown that a manifold with harmonic curvature is equivalent (in four dimensions) to a manifold with harmonic Weyl tensor~\cite{Berger:1969} and constant scalar curvature, or in other words the Ricci tensor is a Codazzi tensor~\footnote{A Codazzi tensor is a symmetric $(0,2)$-type tensor, $T$, satisfying the condition \mbox{$D_X T(Y,Z) = D_Y T(X,Z)$~\cite{Derdzinski01071983}.}}. For prove of these equivalences, see Refs.~\cite{Derdzinski:1985,Besse}.

Equations.~\eqref{SimpleEOM} and~\eqref{harm-curv} are geometrically equivalent to the 
Interestingly, the Eq.~\eqref{SimpleEOM} can be obtained from an effective gravitational Yang--Mills functional action~\cite{stephenson1958quadratic,kilmister1961use,Yang1974},
\begin{equation}
  S_{\textsc{ym}} = \int \Tr \left( \Rif{}{} \we \st \Rif{}{} \right),
\end{equation}
where $\Rif{}{} \in \Omega^2(\Mi, T^*\Mi \otimes T\Mi)$ is the curvature two-form, the operator $\st$ denotes the Hodge star, and the trace is taken on the bundle indices (see Ref.~\cite{bourguignon1982yang}). Albeit this effective theory has been widely studied, it has been considered as a model for a metric field instead of a theory for the connection. Therefore, within the formalism of Palatini, besides Eq.~\eqref{SimpleEOM} an extra field equation appears (for the vielbein field), which strongly constraints the solutions of the gravitational Yang--Mills~\footnote{We thank J.~Zanelli for sharing his personal communications with C.~N.~Yang, and clarify this aspect of the effective model.}. Intriguingly, this effective theory is not renormalizable ---according to the arguments in Refs.~\cite{McGady:2013sga,Camanho:2014apa}---, although it has been discussed in Ref.~\cite{Chen:2010at} that at least the ghost problem can be avoided through the arguments exposed in Refs.~\cite{Kleinert:1987eb,Bender:2007wu,Bender:2008vh,Mannheim:2009zj}.

>>>>

The Eq.~\eqref{SimpleEOM} is related through the second Bianchi identity to the harmonic curvature condition~\cite{bourguignon1981varietes},
\begin{equation}
  \label{harm-curv}
  \nabla_\lambda R_{\mu\nu}{}^\lambda{}_\rho = 0,
\end{equation}
and it can be shown that a manifold with harmonic curvature is equivalent (in four dimensions) to a manifold with harmonic Weyl tensor and constant scalar curvature~\cite{Berger:1969}, or in other words the Ricci tensor is a Codazzi tensor~\footnote{A Codazzi tensor is a symmetric $(0,2)$-type tensor, $T$, satisfying the condition \mbox{$D_X T(Y,Z) = D_Y T(X,Z)$~\cite{Derdzinski01071983}.}}. For prove of these equivalences, see Refs.~\cite{Derdzinski:1985,Besse}.

%% Equations~\eqref{SimpleEOM} and~\eqref{harm-curv} are geometrically equivalent to the 
Notice that Eqs.~\eqref{SimpleEOM} and~\eqref{harm-curv} accept a geometrical interpretation equivalent to that of the field equations of a pure Yang--Mills theory, which in the language of differential forms are
\begin{align}
  \df \Ff*[2] &= 0, & \df \st \Ff*[2] &= 0,
\end{align}
where $\Ff*[2]$ is the field strength 2-form (the curvature 2-form of the connection in the principal bundle), and the operator $\st$ denotes the Hodge star. Now, these Yang--Mills field equations are obtained from the well-known action functional
\begin{equation}
  S_{\textsc{ym}} = \int \Tr \Big( \Ff*[2] \st \Ff*[2] \Big).
\end{equation}

Interestingly, the Eq.~\eqref{SimpleEOM} ---equivalently Eq.~\eqref{harm-curv}--- can be obtained from an effective gravitational Yang--Mills functional action~\cite{stephenson1958quadratic,kilmister1961use,Yang1974}, %constructed as the trace of the 
\begin{equation}
  \label{SKY}
  S_{\textsc{ym}} = \int \Tr \left( \Rif{}{} \st \Rif{}{} \right) = \int \left( \Rif{a}{b} \st \Rif{b}{a} \right),
\end{equation}
where $\Rif{}{} \in \Omega^2(\Mi, T^*\Mi \otimes T\Mi)$ is the curvature two-form, the operator $\st$ denotes the Hodge star, and the trace is taken on the bundle indices (see Ref.~\cite{bourguignon1982yang}).

The gravitational model described by the action in Eq.~\eqref{SKY} is called Stephenson--Kilmister--Yang (or SKY for short). However, the standard interpretation of this model requires a metric tensor. Therefore, a quick analysis of the field equations \`a la Palatini shows that the field equation

Albeit this effective theory has been widely studied, it has been considered as a model for a metric field instead of a theory for the connection. Therefore, within the formalism of Palatini, besides Eq.~\eqref{SimpleEOM} an extra field equation appears (for the vielbein field), which strongly constraints the solutions of the gravitational Yang--Mills~\footnote{We thank J.~Zanelli for sharing his personal communications with C.~N.~Yang, and clarify this aspect of the effective model.}. Intriguingly, this effective theory is not renormalizable ---according to the arguments in Refs.~\cite{McGady:2013sga,Camanho:2014apa}---, although it has been discussed in Ref.~\cite{Chen:2010at} that at least the ghost problem can be avoided through the arguments exposed in Refs.~\cite{Kleinert:1987eb,Bender:2007wu,Bender:2008vh,Mannheim:2009zj}.
